---
title: "Regex"
author: "Micah GVI"
date: "04/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

Import your measurements.csv file from the Week 1 Assignment into an object called MData
```{r}
Mdata<-read.csv("./measurements.csv") #load data from week 1 assignment
head(Mdata)
```

```{r}
Mdata<- Mdata %>% mutate(Sp = sub("(\\w)\\w+","\\1.",Organism)) #creating new column that shortens genus name to the first letter and  period
head(Mdata) #confirm successful column addition

Mdata<- select(Mdata, Sp, Limb.length, Limb.width, Observer, Sp) # reorder columns and replace Organism column with Sp
head(Mdata) # confirm successful column replacement/reorder


```


Use a dplyr command to create a new dataset BUT with Sp column instead of the Organism column, moved to the beginning in place of the original Organism column.

Save the dataset as a new file called MeasShort.csv

Commit these changes using Git in RStudio



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
